Episodic memory: mental time travel or a quantum `memory wave' function?

### 2018-12-18 main.tex
checking in changes
combined movie and fr reinstatement figs

>>>>

\section*{Shared contexts of temporally proximal and remote events}

\begin{figure}[tp] \centering \includegraphics[width=0.75\textwidth]{figs/pres_rec_corrmats} \caption{\textbf{Temporal correlation matrices.}  Each panel displays the timepoint-by-timepoint correlation matrix for presented stimuli (original experience, left panels) and participants' memories of those stimuli (recalled experience, right panels).  }
\label{fig:corrmats}
\end{figure}

\textbf{JRM NOTE: add section on the temporal structure of list-learning vs. naturalistic stimulus, and on the temporal structure of recalls.}
